Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-20 p2/works-inverse.tex
Added TODO comments
Fixed "works" notation for sets

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.

@@

% TODO ???
Also, for all objects where it is defined, $\T{a}\typeeq a$.
As canonical filesystems, commands, sequences, etc.
are subsets of their non-canonical counterparts, 
all propositions proven so far apply to them as well.

As the types of values determine whether a command breaks a filesystem,
we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
From this it follows that
% TODO what's the set of all filesystems?
% TODO:
\begin{mycor}\mlabel{repr_works_is_same}
\begin{gather*}
\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
\end{gather*}
\end{mycor}

@@

\begin{mylem}\mlabel{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
% Use A\cc\{B,C\}
\[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]
\end{mylem}
\begin{proof}
This is trivial unless $\worksmnil{A}$, so we assume that that is the case.
From $B\indep C$ and \cref{combine_independent_sequences} we know
$\worksmbx{B, C}{B\cc C}$.
Based on \cref{repr_works_is_same} this is equivalent to
$\worksmbx{\TB, \TC}{\TB\cc \TC}$.
Since $\TA^{-1}\cc \TA \equiv \emptyseq$, this can also be written as
\[\worksm{\TA^{-1}\cc\{\TA\cc \TB, \TA\cc \TC\}}{\TB\cc \TC}.\]
From \cref{worksextpostfix} we also know that
$\worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA}$.
Combining the last two statements using \cref{r_invmove}
we get
\[ \worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA\cc \TB\cc \TC}, \]
which with \cref{repr_works_is_same} proves the
\namecref{indep_prefix_combine}.
\end{proof}

>>>>

When $\sqs{A}$ or $\sqs{B}$ contains a single sequence,
we leave out the curly brackets and write,
e.g. $A\cc\sqs{B}$ to mean $\{A\}\cc\sqs{B}$,
or $\worksm{A}{B}$ to mean $\worksmbb{A}{B}$.
In particular, we write $\worksmnil{\sqs{A}}$ to mean that
there are filesystems on which all sequences in $\sqs{A}$ are defined.
If $\sqs{A}$ contains a single sequence only, $A$, this is equivalent to $\wrks{A}$.

@@

Also, for all objects where it is defined, $\T{a}\typeeq a$.
As canonical filesystems, commands, sequences, etc.
are subsets of their non-canonical counterparts, 
all propositions proven so far apply to them as well.
-- TODO NEEDED? % TODO

As the types of values determine whether a command breaks a filesystem,
we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
TODO FIND A BETTER WAY OF SAYING THIS -- $\Dom{}$ PRESUPPOSES A SET OF % TODO
ALL FILESYSTEMS THAT IS DIFFERENT FOR CANONICAL OBJECTS.
From this it follows that
\begin{mycor}\mlabel{repr_works_is_same}
\begin{gather*}
\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
\end{gather*}
\end{mycor}

@@

\begin{mylem}\mlabel{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
% Use A\cc\{B,C\}
\[ B\indep C \Rightarrow \worksmbx{A\cc B, A\cc C}{A\cc B\cc C} \]
\end{mylem}
\begin{proof}
This is trivial unless $\wrks{A}$, so we assume that that is the case.
From $B\indep C$ and \cref{combine_independent_sequences} we know
$\worksmbx{B, C}{B\cc C}$.
Based on \cref{repr_works_is_same} this is equivalent to
$\worksmbx{\TB, \TC}{\TB\cc \TC}$.
Since $\TA^{-1}\cc \TA \equiv \emptyseq$, this can also be written as
\[\worksm{\TA^{-1}\cc\{\TA\cc \TB, \TA\cc \TC\}}{\TB\cc \TC}.\]
From \cref{worksextpostfix} we also know that
$\worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA}$.
Combining the last two statements using \cref{r_invmove}
we get
\[ \worksmbx{\TA\cc \TB, \TA\cc \TC}{\TA\cc \TB\cc \TC}, \]
which with \cref{repr_works_is_same} proves the
\namecref{indep_prefix_combine}.
\end{proof}
